---
title: "R Notebook"
output: html_notebook
---

Load csv and perform exploratory data analysis 

```{r}
getwd()
file <- "CSVs\\Kickstarter.csv"
convert(file, "kickstarter.json")
eda <- read.csv(file)

```
Load libraries
```{r}
library(anytime)

getwd()
file <- "CSVs\\Kickstarter.csv"

eda <- read.csv(file)

eda2 <- eda
eda2$source_url <- gsub("https://www.kickstarter.com/discover/categories/", "", eda2$source_url)
eda2$source_url <- gsub("%20", " ", eda2$source_url)
#print(eda2$source_url)
Cat<-data.frame(do.call('rbind', strsplit(eda2$source_url, '/', fixed=TRUE)))
eda2$MainCategory <- Cat$X1
eda2$SubCategory <- Cat$X2
eda2$created_at <- anytime(eda2$created_at)
eda2$deadline <- anytime(eda2$deadline)
eda2$launched_at <- anytime(eda2$launched_at)
eda2$state_changed_at <- anytime(eda2$state_changed_at)
#removed json columns -- couldn't figure out how to parse it as JSON
drops <- c("category","creator","location","photo","profile","source-url","urls")
eda2 <- eda2[,!names(eda2) %in% drops]
# result is in time format
eda2$campaignDurationDays <- round(difftime(eda2$deadline,eda2$launched_at, units = "days" ))
head(eda2,5)


head(eda,1)
cat_raw <- as.JSON(eda$category)
str(cat_raw)
is.vector(cat_raw)

data_raw <- jsonlite::fromJSON(eda$category)
glimpse(data_raw, max.level = 3, list.len = 4)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.
```{r}
#import json
tryjson <- fromJSON(txt="kickstarter.json")
str(tryjson)
```

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

```{r}
eda2 <- eda
eda2$source_url <- gsub("https://www.kickstarter.com/discover/categories/", "", eda2$source_url)
eda2$source_url <- gsub("%20", " ", eda2$source_url)
#print(eda2$source_url)
Cat<-data.frame(do.call('rbind', strsplit(eda2$source_url, '/', fixed=TRUE)))
eda2$MainCategory <- Cat$X1
eda2$SubCategory <- Cat$X2
eda2$created_at <- anytime(eda2$created_at)
eda2$deadline <- anytime(eda2$deadline)
eda2$launched_at <- anytime(eda2$launched_at)
eda2$state_changed_at <- anytime(eda2$state_changed_at)
#removed json columns -- couldn't figure out how to parse it as JSON
drops <- c("category","creator","location","photo","profile","source-url","urls")
eda2 <- eda2[,!names(eda2) %in% drops]
# result is in time format
eda2$campaignDurationDays <- round(difftime(eda2$deadline,eda2$launched_at, units = "days" ))
head(eda2,5)

```

```{r}

```

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
